The pollination trade-off

### 2019-04-09 paper/manuscript.Rmd
Cosmetic changes to title page

---
title: "The pollination trade-off"
author: "E. Fernando Cagua^1^, Hugo J. Marrero^2^, Jason M. Tylianakis^1^, Daniel B. Stouffer^1^"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

@@

@@

**Keywords:** X,Y,Z

@@

**Author for correspondence:** E. Fernando Cagua (efc29@uclive.ac.nz) - +64 20 4026 8153

**Authors' email addresses:** Hugo J. Marrrero (hugomarrero@gmail.com); Jason M. Tylianakis (jason.tylianakis@canterbury.ac.nz); Daniel B. Stouffer (daniel.stouffer@canterbury.ac.nz)

>>>>

---
title: "The pollination trade-off"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

@@

<!-- ^a^ [efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz); ^b^ [hugomarrero@gmail.com](hugomarrero@gmail.com); ^c^ [jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz); ^d^ [daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz) -->

@@

**Keywords:** X,Y,Z (up to 10)

@@

**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153)
